Usage metrics

### 2020-12-07 inst/analysis/usage_metrics.Rmd
Update usage metrics

r("nb eval call sites", nb_ev_call_sites)
r("packages no calls to eval", nb_no_calls_to_eval)
r("nb median call sites", median_call_sites$med)
r("max call sites", max_packages$nb_call_sites)
r("max call sites package", max_packages$eval_source)
r("at least one call site", nrow(packages_at_least_one_call_site))
```

>>>>

r("nb eval call sites", nb_ev_call_sites)
r("nb one call site", nb_packages_one_call_site)
r("packages no calls to eval", nb_no_calls_to_eval)
r("nb median call sites", median_call_sites$med)
r("max call sites", max_packages$nb_call_sites)
r("max call sites package", max_packages$eval_source)
r("at least one call site", nrow(packages_at_least_one_call_site))
```
